Smart Sanitizing Mobile Robot using Ultra-violet Sterilization Technology: A Prototype

### 2021-01-15 paperFLAIRS34-LatexCode/paperFLAIRS2021-V1.tex

\section{Existing Sanitizing Robots} 
\section{Existing Sanitizing Robots} 
\label{sec:Literature}
There are many ways of transmitting infections disease, and studies have shown that the greatest cause of contact surface such as: remote control, door handles or cabinets, a button to call for help, etc. UV-C disinfection robot provides an economical and effective measure in limiting the spread of bacteria.  UV-C disinfection robot provides an economical and effective measure in limiting the spread of bacteria. When bacteria are exposed to UV-C light of their DNA absorbs light energy and causes cell damage that prevents new infecting others. The robot is controlled by the medical staff and the time for which disinfect a room is 10–15 min depending on the size of the room.

>>>>

-The design and development of a class of mobile robots in sterilizing indoor
-environments, hospitals, offices, and other indoor spaces, for example, have
-received a special attention in recent years, especially due to Coronavirus
-diseases - 2019 (COVID-19)\todo[inline]{Reference}. Recently, a class of mobile robots has been
-developed to sterilize indoor spaces using UV-C sterilization
-technology~\todo[inline]{Reference}. Most of the mobile robots developed so far in
-sanitizing indoor environments either rely on fixed-mount UV-tube or sprayers to
-disinfect areas much like a conventional cleaning robot. It is worth noting
-that, not many sanitizing robots use UV lights to disinfect robot based on the
-map of the indoor operating environment. In this paper, we develop a prototype
-of a modular and cost-effective mobile robot, where robot has the ability to
-smartly decide on the indoor space to  be sterilize based on the map. The map of
-the environment is created using sensor fusion technology much like what
-conventional autonomous robots do using range and vision sensors.
\section{Existing Sanitizing Robots} 
\section{Existing Sanitizing Robots} 
\label{sec:Literature}
There are many ways of transmitting infections disease, and studies have shown that the greatest cause of contact surface such as: remote control, door handles or cabinets, a button to call for help, etc. UV-C disinfection robot provides an economical and effective measure in limiting the spread of bacteria.  UV-C disinfection robot provides an economical and effective measure in limiting the spread of bacteria. When bacteria are exposed to UV-C light of their DNA absorbs light energy and causes cell damage that prevents new infecting others. The robot is controlled by the medical staff and the time for which disinfect a room is 10–15 min depending on the size of the room.
